---
title: "Problems and Solutions to Compile a PDF Version of Advanced R"
author: "Boyi Zhang"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set( eval = FALSE)
```

\newpage
# At the begining

Clone the program (https://github.com/hadley/adv-r). 

Updating all the package and Software, like Rstudio, Texlive, that I can do. 

We generate the gitbook (html version) first, then pdf book.

\newpage
# gitbook
For html book, compiling with the code 
```{r}
bookdown::render_book("index.Rmd", "bookdown::gitbook")"
```

## Reading problems with "contribute.csv"
There is no specific error reason about it, but some character cannot be distinguished correct when I saw the error message, such as Chinese Character, French Character, etc.

The reason is just because the encoding problem. Add a encode parameter in the line 224 of **Introduction.Rmd**, like this:

`contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, encoding = "UTF-8")`

## For missing packages.
For majority of the packages, you can use 
```{r}
intall.package()
``` 
to install package.

## For missing Fonts.
Font is quiet different, there are two fonts, `Inconsolata`, `AndaleMono`, I missed.

Downloads the Opentype file(.otf), put it into latex folder (C:/texlive/2020/texmf-dist/fonts/opentype/public)

Downloads the Truetype file(.ttf), put it into latex folder  (C:/texlive/2020/texmf-dist/fonts/truetype/public)

## Cannot install emo and sloop package from CRAN.
It is because the package are special sources, we need to install the Rtools40 to install it. Code like this

```{r}
devtools::install_github("hadley/emo")
```

## in system(cmd) "make" not found
For this error message, just because install Rtools40 via wizard is not enough, we still should type the code

```{r}
writeLines('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', con = "~/.Renviron")
```

## No such file or directory
Redirect the folder by Using the following code. It's depends on message content, for me

`sh: c:/Rtools/mingw_64/bin/g++: No such file or directory`

In this case, I use

```{r}
Sys.setenv(BINPREF = "C:/Rtools/mingw$(WIN)/bin/")
Sys.setenv(PATH = paste("C:/Rtools/bin", Sys.getenv("PATH"), sep=";"))
```

to redirect.

\newpage
# pdf_book
For pdf book, compiling with the code 
```{r}
bookdown::render_book("index.Rmd", "bookdown::pdf_book")
```
## LaTeX Error: Environment sidebar undefined.
Upgrade the rmarkdown through github, cannot directly upgrade via CRAN.
```{r}
devtools::install_github('rstudio/rmarkdown')
```
and upgrade ALL (use $1^{st}$ option), then all set.

## Failed to install 'rmarkdown' from GitHub:cannot remove prior installation of package ‘digest’
This error occurred when I upgrade the rmarkdown.
Use command
```{r}
.libPaths()
```
to search the folder path, find 'digest' folder and delete it manipulatively.

\newpage
# Overall
As for pdf book generated, there are several warning messages about multiply defined. It may not affect the final book I generated. So, just omit it.

The book is compiled in the "adv-r/_book" folder.
